\chapter{Strategic alignment report}
The following section will cover the strategic information on DANX. First it will cover the strategic goals of DANX, their target group, their value propositions, and the rest of the business canvas. 
Then the report will talk about the environment and make a SWOT and competitor analysis to find strong and weak sides of DANX, which will be analyzed later in the in-depth phase.
Next it will describe the work domains and the different departments affected by our solution. The two major departments are the IT department and the operation department.

\section*{Business strategy}
In this section DANX’s business strategy is analyzed. It contains information about key values, goals and challenges.
DANX has a general business strategy aimed at ensuring that their customers get their spare parts fast and on time, and also ensure good support whenever there is a problem.

\subsection{Canvas}

[CANVAS]


DANX's values of fast delivery, overnight delivery and guaranteed pre 7am delivery are key values for DANX in order to keep their customers happy and keep growing. These values are only possible to their extent because of DANX’s key resources, Field Stock Locations and  Pick-up/Drop-off locations, which greatly help DANX drivers to deliver fast and on time, and it allows customers to even pick up spare parts themselves. The two last mentioned values are what separates DANX from the herd of logistics companies and gives them an edge in regards of companies mentioned in the customer segment. Companies which require fast and/or reliable delivery or just need external storage of spare parts are those that DANX focus on and will try to acquire.
DANX also has key values of fast and efficient IT support, as well as fast implementation of new customers into DANX's system, and even if new customers' have not yet been integrated into DANX's IT system, DANX will start delivery from the day new customers' former contract expired. These values are more focused on good customer service which is an important resource for DANX. Satisfied customers helps DANX gain new customers with mouth to mouth between companies.

\subsection{Goals}
DANX has a general growth strategy ie. they want to gain 25-30 customers each year. Starting this year DANX is focusing on profit. Last year they had a profit of 10 million danish kroners, and a revenue of 250 million DKK. This year, It is expected that the revenue will increase to at least 300 million DKK and the profit to 20 million DKK. The overall goal is to have a revenue of at least 500 million DKK and a profit of eight to ten percent within 3-4 years. \\

Since one of DANXs key selling points is their pre 7 am delivery, they strive to deliver plus 99\% of the packages before 7 am.

\subsection{Values}
Reliability, Equality, Quality, Flexibility, Creativity, Availability and Pride are the seven values that DANX operate with.

\begin{description}

\item[Reliability] DANX keeps their promises, correct their mistakes and proactively informs their customers.
\item[Equality] Customers, partners and colleagues are all equals and treated with the same respect.
\item[Quality] Customers are not taken for granted. 100\% is strived for in everything that is done. This ensures that customers of DANX can live up to their customers high expectations.
\item[Flexibility] - All employees and partners are expected to have a flexible mindset.
\item[Creativity] As pioneers DANX has to think outside the box to create solutions for the needs of their customer. DANX is constantly looking for ways to improve.
\item[Availability] DANX ensures the availability of all their customers spare parts through each employee’s personal care
\item[Pride] DANX takes pride in in everything they do. They are proud of their customers, company and their people.

\end{description}

\subsection{Business model}

\subsection{Challenges and problems}
It is cumbersome for the management of DANX to analyze the problems the customers requests help with and how often a certain problem occurs. Furthermore it is difficult to collect information about a certain customer, e.g. how often they request help with a problem and what type of problems they need help with. The information can for example be used to evaluate if the pricing of the customer is right or detect if multiple customers have the same problem due to a difficult or unclear work practice. \\

The structure of requests for help regarding internals at DANX is non existent, which leads to Lasse using up to several minutes identifying the actual problem. If the requests for help followed a clear cut structure, then it would be a lot easier to identify the actual problem. \\

Many of the companies DANX is delivering spare parts to, have their main storage department in either Holland or Germany. When a customer orders a spare part with pre 7 am. delivery, the spare part is picked up at their storage department by DANX and shipped to where the customer needs it. If the spare part is going to another country than Denmark the part is transported by plane some of the way. This is a potential challenge because the plane can be delayed or have no room for cargo.

Stemme02 - 24:47, DANX henter i holland og leverer i danmark inden klokken 7.
stemme 002 - 43:00, Henter i Salzgitter syd for hannover 15:30 og leverer nord for Stockholm inden 7 næste morgen
	


\section*{Environment}
In this section the environment is analyzed. Firstly the competitors of DANX are investigated and secondly a SWOT analysis is conducted.
	
\subsection{Competitor analysis}
\subsubsection{Competitors}
DANX’s main competitor is a special service within TNT called TNT innight.
Just as DANX, TNT innight provides delivery of items within 7 am the following day.
TNT also targets some of the same segments as DANX such as 

\begin{itemize}
\item The car industry where they deliver spare parts to manufacturers and repair shops.
\item The medical industry where they make deliveries to hospitals
\item Farmers during the harvest season
\end{itemize}

Some of the advantages TNT has:
\begin{itemize}
\item A larger company and brand
\item Their own flight routes from Bruxelles to Jönköping, Helsinki, Oslo, and Billund
\end{itemize}

A larger brand makes the company more trustworthy, and ease the process of getting new customers. This is a threat to DANX seeing that DANX wants to get more customers as a part of their business goal [Reference to business goals here]

Their own flight routes are a major factor as this grants faster delivery time, and a better quality compared to DANX. If one if DANX flights are canceled the goods are likely to be delayed, whereas this will not happen to TNT.

Some of the disadvantages TNT has:
\begin{itemize}
\item External IT company that is responsible for integrating TNT’s customers [Reference til Bob]
\item Due to TNT’s size the prices may be slightly higher.
\end{itemize}

The external IT company means that delays may arise when integrating a customer, further more it can also take longer because the external company may have other orders in queue. This can lower the quality of the service.
The prices for TNT may be slightly higher than DANX due to their size. This can be due to the extra services such as the flight routes that TNT has. \\

Another new competitor is HIT. This is a relatively new competitor which started 1st September 2013. HIT provides the same service as DANX namely pre 7 am delivery during the night. 
One of HIT’s advantages is they have a lot of companies to back them up such as posten.se and Postdanmark A/S. A disadvantage is that the company is new started and thus doesn’t have any good reputation which is important in this niche. Furthermore a newly started company will not have much experience compared to the existing ones on the market, which may lead to worse quality.
As HIT is a newly started company they should have easier establishing company strategies, KPIs, and goals compared to DANX, which lacks this information.  

\subsubsection{Substitution}
Another competitor with a possible substitutional service would be FedEx. FedEx is offering a similar service on a national basis where you can send a national priority package. It will usually be delivered within 12 am the following work day, depending on where the package is going from and to. While this is not entirely the same service as DANX provide, some customers who have a need to send national packages may choose this option, seeing that the time may be the same as DANX if they happen to be shipping at that time, and that the price may be slightly cheaper. The customer is able to check the time of delivery when they request the delivery on FedEx’s website. \\

\subsubsection{New market entrants}
There are already a few existing companies which in the future, might be interested in expanding their service and provide delivery before 7 am the next day. Some of those companies are DHL and UPS.
This would require a lot of internal restructuring on DHL and UPS, but seeing that the only major players are DANX and TNT it should be possible to gain some of the market share. The companies would also have to change their goals to aim for a lot higher quality when delivering pre 7 am. They also have advantages in form of their size, brand, and current customer base.\\

Instead of going after DANX’s customers they could also be targeting new segments such as southern Europe. There may be complications entering this market, seeing DANX is in the ELSA partnership, which means their partners operate in the southern part of Europe.

\subsection{SWOT}

\begin{tabular}{ | p{6.4cm} | p{6.4cm} | }
\hline
\textbf{Strengths} & \textbf{Weaknesses} \\ \hline
Customer integration within 3 days & No documentation on customer support requests \\ \hline
Lots of PUDOs and field stock locations & No documentation on customer support requests \\ \hline
Strong brand & No documentation on the work being done in the IT development department \\ \hline
Lots of small subcontractors & No KPIs or goals for the IT department \\ \hline
Direct support & No KPIs in the operation department \\ \hline
\textbf{Opportunities} & \textbf{Threats} \\ \hline
Gain work experience at ELSA partners & Flight routes \\ \hline
 & \\ \hline
\end{tabular}
Strengths
Weaknesses
Customer integration within 3 days
No access to customer API’s
Lots of PUDOs and field stock locations
No documentation on customer support requests
Strong brand
No documentation on the work being done in the IT development department 
Lots of small subcontractors
No KPIs or goals for the IT department
Direct support
No KPIs in the operation department
Opportunities
Threats
Gain work experience at ELSA partners
Change in flight or ferry routes





\textbf{Strengths}
\begin{itemize}
\item Customer integration within 3 days is a lot better than their competitors. When a customer’s previous contract expires they need a new one as soon as their old one expires, and if the other companies cannot provide that due to the IT solution not being ready on time, they will lose a customer to (possibly) DANX.
\item PUDOs and field stock locations are expensive to establish. Fortunately DANX had a customer that was willing to pay for them to be set up. This means DANX now can offer this service to other customers as well in order to improve their service.
\item Strong brand works as a trust factor when trying to gain new customers. As we saw earlier [reference to competitors - new market entrants] in the new market entrants there may be quite a few, and the brand will be a strong strength for DANX.
\item Lots of small subcontractors means it is easy for DANX to remove and add new sub contractors in busy periods/seasons. 
\item Direct support is very important as a part of the quality and service DANX provides to their customers. This allows the customer to phone or email Lasse directly with questions related to the integration between DANX’s IT systems and the customers’ IT systems.
\end{itemize}

\textbf{Weaknesses}
\begin{itemize}
\item No access to customer APIs means that DANX has to make multiple systems. This leads to a lot of manuals for the employees at DANX, and getting to know all the systems for a new employee can be a slow process. If DANX had access to customer APIs it would be easier to integrate the different systems into a single one.
\item The lack of documentation in the IT department makes it impossible for managers to check what is actually being done, if the work is being done on time and so on.
It can also be a problem if a system is developed and needs to be changed 3 months later. This can result in a complete re-written module for that system [reference to the interview where lahib claims this]  
\item No documentation for customer support means that it is impossible for DANX to track how many requests they receive, how fast they are resolved, and how much support the individual customer requests.
This makes it hard to detect any weaknesses in the customer support which is crucial for the service level.
\item No KPIs for the IT department and the operation department means that they have no indication if things are going good or bad. It can also serve as a de-motivating factor to the employees as they don’t know if they are doing good or bad. It also makes it hard to figure out why it is going good or bad in the individual department.
\end{itemize}

\textbf{Opportunities}
\begin{itemize}
\item DANX can gain free experience from their ELSA partners which they have not done yet. This is a way to learn more about alternate methods which may be better, and make them stand stronger on the northrend market. [Reference til GERT’s første interview hvor der snakkes om ELSA]
\end{itemize}


\textbf{Threats}
\begin{itemize}
\item The lack of own flight routes means that DANX is dependant that the flights are not delayed, and that they accept DANX’s cargo. If they do not the delivery will be delayed which causes bad reputation and quality.
\end{itemize}




\section*{Work Domains}

DANX Nordic is situated in Vallensbæk, Denmark. The company has organisations in Sweden, Norway, Finland \& Denmark.\\

Within each organisation there is a flat structure, where one regional director is sitting at the top, followed by an operations manager and a sales manager. At the bottom we have a number of contracted drivers responsible for the final delivery of the spare parts - these are independent of DANX but are hired to carry out their bidding.\\

The nordic branch is different from the regional organisations in the sense that it has an IT-department and a marketing department. These are used by all regional organisations and the centralisation of these aligns DANX different departments both in IT as well as marketing and customer relations.\\

For this project the important departments to consider are:

\subsection{IT department}
The IT department at DANX consists of Lasse, the Head of IT development department, and 3 employees. The department develops IT systems, such as the TrackIT system, which is used in all of DANX's departments and is developed by the IT development department. They also do integration with customers systems. When DANX gets a new customer the IT department make sure that it will only take a few days before they have fully implemented the integration between DANX’s IT systems and the customer’s IT system, in order to properly create new contracts and shipments with the new customer. The department also develops any new software necessary or required by the operation or if possible, requested by an employee. \\

They are also responsible for any internal and customer support related to software inside DANX, such as the TrackIT system and the software implemented in order to connect and communicate with customers systems. This support helps with using the systems and correct bugs when they occur. They give support by email and phone, and if it is customer support, the operational department will typically have received it first and read it through and then forwarded it to the it department afterwards if it is not something they can handle themselves. \\

The it department is an important work domain to focus on as they are the main support for customers and internal staff regarding complications with internal systems, so any solutions proposed by this project will be based upon the workflow of the it department and it will likely have some impact on the work processes currently in use.\\

Lasse is a key resource for DANX seeing that he is responsible for integrating new customers. This is a very important activity for DANX and one of it’s key strengths, which means that it could conflict with the business goals to gain new customers. If Lasse is the only person able to integrate them it could be a bottleneck for the business goals, or DANX could lower their quality with customer integration. Lowering the standards would mean DANX lost a huge strength compared to their competitors, thus not a good option.


\subsection{Operational department}
The operational department consists of Gert Phillipsen, which is the operational manager, and approximately 50 employees. \\
 
The operations department is the main department, both in regards to internal coordination of packages as well as customer support requests. They propagate support requests when they are unable to fix the issues. 
The control tower is part of the operational department and is always open. It serves as a reliable contact for their customers and ensures that any problems that may hinder delivery of spare parts is addressed. \\

Currently the operational department has no KPIs or business goals which is preventing the management, Gert, and the employees for knowing when the department is doing good or less good. This is a potential problem seeing that the operation department is representing DANX when handling customer issues. \\

Aside from the customer support the operation is also responsible for managing the different sub contractors, either when something goes wrong, or if a driver is insecure on how to proceed. 


\subsection{Conclusion}
Seeing that the IT department is a huge bottleneck for DANX it might be worth analyzing in the in-depth analysis. The huge problem is that Lasse is the only person who knows how to integrate new customers with DANX systems, and is the only person with insight in those integrations. This means that as DANX grows the workload on Lasse will climb to a point where he can no longer keep up.
Unfortunately it is very difficult to train/employ an additional “Lasse”, seeing that Lasse needs to spend time on this, that he doesn’t have. It is not feasible to extend the deadlines of Lasse’s work as customers need it right away, and that this is one of DANX’s main strengths. 

\subsection{IT support department}
DANX’s IT support department consist of 2 employees. Their job is to maintain internal support regarding hardware problems and provide internal support.



(another department which uses trackit)

Storage unit
The storage unit is responsible for keeping stock records. When one or more goods are sent to the customer the storage unit is responsible for putting this into TrackIT.