\documentclass[pdftext, 12pt, a4paper]{report}

\usepackage[toc, page]{appendix}
\usepackage{xcolor, colortbl}
\usepackage{color}
\usepackage{multirow}
\setlength{\parindent}{0cm}

\begin{document}

%\title{DanX}
%\date{}
%\author{		Mikkel Hvilshøj Funch \\ mhvf@itu.dk
%		\and 	Andreas Precht Poulsen \\ appo@itu.dk
%		\and 	Mark Thorhauge \\ marth@itu.dk
%		\and 	Mikkel Thomsen \\ mikt@itu.dk
%		\and 	Ivan Naumovski \\ inau@itu.dk		
%		}
%\maketitle
%\tableofcontents

\section*{Contract}
The project is conducted for learning purposes in order to simulate the actual work done according to the MUST method for the course Business Processes and Organisation, Fall 2013, at the IT university of Copenhagen. The project will produce a business case, but will not solve the investigated problem. The project will be supervised by Nina Boulus-Roedje and Elisabeth Broe Christensen.

\section*{Purpose of project charter}
The project charter defines the objective of the project and what work has to be done to reach this objective, as well as which resources the project team needs from DANX and which deliverables the company will receive.

The project charter serves as a contract between the project team and DANX, such that everyone involved in the project has the same view of the vision, assumptions, planning, resource consumption and boundaries of the project.


\section*{Premise}
\subsubsection*{Scope}
The scope of the project includes internal communication, not communication with customers and others outside of DANX. In other words this means that customers will still have the same high degree of service and availability from all IT-staff, because the proposed solutions do not seek to change the way customers communicate with the IT-staff of DANX. 

\subsubsection*{Critical preconditions}
\begin{itemize}
	\item It must be possible for the project group to observe how the work flow of DANX is on a regular day.
	\item The project group can conduct interviews with persons relevant to the assignment.
	\end{itemize}
\newpage
\subsection*{Assignment and Objective}
The employees of DANX can not access error reports from a specific customer, because the reports are not documented or do not contain information that identify the customer. This hinders potential evaluation of support given to a customer. \\ \\
How can employees of DANX access documentation for customer support? \\ \\
The problem is solved when at least one employee of DANX can access documentation for customer support within two minutes.

\subsection*{Agreements and coordination}
The project groups contact person in DANX is marketing manager Malene Vig Hjarnaa. she will be responsible for providing contact to other employees inside the company and making the required resources available. Malene can be contacted on mhj@danx.dk, during regular office hours, i.e. 0900-1600. The contract extends to 16. december 2013.
\\ \\ \\ \\ \\ \\
\textbf{Signatures}
\\ \\ \\ \\
\underline{\hspace{9em}} \hspace*{12.8em} \underline{\hspace{9em}}
\\
Malene Vig Hjarnaa \hspace*{13em} Mark Thorhauge
\\ \\ \\
Date \underline{\hspace{9em}}
\newpage
\begin{tabular}{ | p{3.8cm} || p{4.5cm} | p{4.5cm} | }
\hline
\textbf{Activity} & \textbf{Date/Time} & \textbf{Actors}\\ \hline \hline
Interview and presentation & 24.09.2013 09:00 - 12:00 & Malene Hjarnaa, Gert Philipsen, Lasse Trier \\ \hline
Interview & 23.10.2013 10:00 - 10:45 & Lasse Trier, Lahib \\ \hline
Interview & 13.11.2013 10:00 - 11:00 & Lasse Trier, Jakob \\ \hline
Interview & 20.11.2013 10:00 - 11:00 & Lasse Trier \\ \hline
Interview & 27.11.2013 10:00 - 11:00 & Lasse Trier \\ \hline
Interview & 29.11.2013 10:00 - 11:00 & Gert Philipsen \\ \hline
\end{tabular}

\end{document}